---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data



```{r}
if(!file.exists("activity.zip")) {
        temp <- tempfile()
        download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",temp)
        unzip(temp)
        unlink(temp)
}

data <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?


```{r}
steps_day <- aggregate(steps ~ date, data, sum)
hist(steps_day$steps, main = paste("Total Steps per Day"), col="red", xlab="Number of Steps")
```

```{r}
rmean <- mean(steps_day$steps)
rmedian <- median(steps_day$steps)
```

The mean is 10766 steps, the median is 1765.


## What is the average daily activity pattern?


Time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)


```{r}

steps_interval <- aggregate(steps ~ interval, data, mean)

plot(steps_interval$interval,steps_interval$steps, type="l", xlab="Interval", ylab="Number of Steps",main="Average Number of Steps per Day by 5 min intervals")


```

The 5-minute interval, on average across all the days in the dataset, containing the maximum number of steps:

```{r}
max_interval <- steps_interval[which.max(steps_interval$steps),1]

```





## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
